Market simulator

### 2020-10-28 analysis/05_market_simulator.Rmd
figuring out a way to automatically update data with actionButton
Cleaned up code for all the new rendered objects for uploadable configurations

# Initial organization configuration
# organization_data <- read_csv(
#   here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
# )

organization_values <- reactiveValues()

organization_data <- reactive({
  if (is.null(input$org_update$datapath)) {
    organization_data <- read_csv(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
    # organization_values$file_name = "organization_config01.csv"
    # organization_values$file_type = "csv"
    # organization_values$file_size = file.size(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
    # organization_values$file_path = here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
  } else {
    organization_data <- read_csv(input$org_update$datapath)
    # organization_values$file_name = input$org_update$name
    # organization_values$file_size = input$org_update$size
    # organization_values$file_type = input$org_update$type
    # organization_values$file_path = input$org_update$datapath
  }
})

# Initial persona configuration
persona_data <- read_csv(
  here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
)

```

```{r organization-reactive-table}

# Assign level labels
org_table <- data.frame(
  levels = c(
    # Organization
    "Amnesty International",
    "Greenpeace", 
    "Oxfam", 
    "Red Cross",
    # Issue area
    "Environment", 
    "Human rights",
    "Refugee relief",
    # Financial transparency
    "Engages in financial transparency",
    # Financial accountability
    "Engages in financial accountability",
    # Funding sources
    "Handful of wealthy private donors", 
    "Government grants",
    # Relationship with host government
    "Criticized by government",
    "Under government crackdown"
  )
)

@@

  # Organization 4
  org_table$org4_value <- 0
  org_table$org4_value[org_table$levels %in% input$org4_org] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_issue] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_fin_trans] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_fin_account] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_funding] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_host_gov] <- 1
  org_table
})

```

@@

  # Persona 3
  per_table$per3_value <- 0
  per_table$per3_value[per_table$levels == 'Intercept'] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_national_news] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_international_news] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_news_medium] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_follow_gov] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_travel_developing] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_political_pref] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_institution_trust] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_others_charitable] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_worship_attendance] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religion_importance] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religion] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_charity_importance] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_trust_in_charity] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_donation_frequency] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_donation_amount] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_volunteer_12] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_volunteer_frequency] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_personal_activism] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_family_activism] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religious_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_sport_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_art_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_labor_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_political_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_environmental_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_professional_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_humanitarian_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_consumer_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_other_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_gender] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_marital_status] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_education] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_income] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_race] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_age] <- 1
  per_table
})

# per_update <- reactiveValues(data = NULL)
# per_update$data <- per_table

```

@@

```{r org1-inputs}
# Naming
textInput(
  "org1_name",
  label = "Organization Name:",
  value = "Organization 1",
  placeholder = "Enter Organization Name",
  width = "450px"
)
# Organization
renderUI({
  org_data = organization_data()

  selectInput(
    "org1_org",
    label = "Organization:",
    choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
    # selected = "Red Cross",
    # selected = as.character(organization_data[1:4,][which(organization_data[1:4,2] == 1), 1]),
    selected = as.character(org_data[1:4,][which(org_data[1:4,2] == 1), 1]),
    width = "450px"
  )

})

# Issue area
renderUI({
  org_data = organization_data()

  selectInput(
    "org1_issue", 
    label = "Issue Area:",
    choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
    # selected = "Emergency response",
    selected = ifelse(
      # sum(organization_data$data[5:7,2]) == 0, "Emergency response",
      # as.character(organization_data$data[5:7,][which(organization_data$data[5:7,2] == 1), 1])
      sum(org_data[5:7,2]) == 0, "Emergency response",
      as.character(org_data[5:7,][which(org_data[5:7,2] == 1), 1])
    ),
    width = "450px"
  )

})

# Financial transparency
renderUI({
  org_data = organization_data()

  selectInput(
    "org1_fin_trans",
    label = "Financial Transparency:",
    choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
    # selected = "Engages in financial transparency",
    selected = ifelse(
      # sum(organization_data$data[8,2]) == 0, "Doesn’t engage in financial transparency",
      # as.character(organization_data$data[8,][which(organization_data$data[8,2] == 1), 1])
      sum(org_data[8,2]) == 0, "Doesn’t engage in financial transparency",
      as.character(org_data[8,][which(org_data[8,2] == 1), 1])
    ),
    width = "450px"
  )

})

# Financial accountability
renderUI({
  org_data = organization_data()

  selectInput(
    "org1_fin_account",
    label = "Financial Accountability:",
    choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
    # selected = "Engages in financial accountability",
    selected = ifelse(
      # sum(organization_data$data[9,2]) == 0, "Doesn’t engage in financial accountability",
      # as.character(organization_data$data[9,][which(organization_data$data[9,2] == 1), 1])
      sum(org_data[9,2]) == 0, "Doesn’t engage in financial accountability",
      as.character(org_data[9,][which(org_data[9,2] == 1), 1])
    ),
    width = "450px"
  )

})

# Funding sources
renderUI({
  org_data = organization_data()

  selectInput(
    "org1_funding",
    label = "Funding Source:",
    choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
    # selected = "Many small private donations",
    selected = ifelse(
      # sum(organization_data$data[10:11,2]) == 0, "Many small private donations",
      # as.character(organization_data$data[10:11,][which(organization_data$data[10:11,2] == 1), 1])
      sum(org_data[10:11,2]) == 0, "Many small private donations",
      as.character(org_data[10:11,][which(org_data[10:11,2] == 1), 1])
    ),
    width = "450px"
  )

})

# Relationship with host government
renderUI({
  org_data = organization_data()

  selectInput(
    "org1_host_gov",
    label = "Relationship With Host Government",
    choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
    # selected = "Friendly relationship with government",
    selected = ifelse(
      # sum(organization_data$data[12:13,2]) == 0, "Friendly relationship with government",
      # as.character(organization_data$data[12:13,][which(organization_data$data[12:13,2] == 1), 1])
      sum(org_data[12:13,2]) == 0, "Friendly relationship with government",
      as.character(org_data[12:13,][which(org_data[12:13,2] == 1), 1])
    ),
    width = "450px"
  )

})
```

@@

# Organization
renderUI({
  org_data = organization_data()

  selectInput(
    "org2_org",
    label = "Organization:",
    choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
    # selected = "Red Cross",
    selected = as.character(org_data[1:4,][which(org_data[1:4,3] == 1), 1]),
    width = "450px"
  )

})

# Issue area
renderUI({
  org_data = organization_data()

  selectInput(
    "org2_issue", 
    label = "Issue Area:",
    choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
    # selected = "Environment",
    selected = ifelse(
      sum(org_data[5:7,3]) == 0, "Emergency response",
      as.character(org_data[5:7,][which(org_data[5:7,3] == 1), 1])
    ),
    width = "450px"
  )

})

# Financial transparency
renderUI({
  org_data = organization_data()

  selectInput(
    "org2_fin_trans",
    label = "Financial Transparency:",
    choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
    # selected = "Engages in financial transparency",
    selected = ifelse(
      sum(org_data[8,3]) == 0, "Doesn’t engage in financial transparency",
      as.character(org_data[8,][which(org_data[8,3] == 1), 1])
    ),
    width = "450px"
  )

})

# Financial accountability
renderUI({
  org_data = organization_data()

  selectInput(
    "org2_fin_account",
    label = "Financial Accountability:",
    choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
    # selected = "Engages in financial accountability",
    selected = ifelse(
      sum(org_data[9,3]) == 0, "Doesn’t engage in financial accountability",
      as.character(org_data[9,][which(org_data[9,3] == 1), 1])
    ),
    width = "450px"
  )

})

# Funding sources
renderUI({
  org_data = organization_data()

  selectInput(
    "org2_funding",
    label = "Funding Source:",
    choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
    # selected = "Many small private donations",
    selected = ifelse(
      sum(org_data[10:11,3]) == 0, "Many small private donations",
      as.character(org_data[10:11,][which(org_data[10:11,3] == 1), 1])
    ),
    width = "450px"
  )

})

# Relationship with host government
renderUI({
  org_data = organization_data()

  selectInput(
    "org2_host_gov",
    label = "Relationship With Host Government",
    choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
    # selected = "Friendly relationship with government",
    selected = ifelse(
      sum(org_data[12:13,3]) == 0, "Friendly relationship with government",
      as.character(org_data[12:13,][which(org_data[12:13,3] == 1), 1])
    ),
    width = "450px"
  )

})

```

@@

# Organization
renderUI({
  org_data = organization_data()

  selectInput(
    "org3_org",
    label = "Organization:",
    choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
    # selected = "Red Cross",
    selected = as.character(org_data[1:4,][which(org_data[1:4,4] == 1), 1]),
    width = "450px"
  )

})

# Issue area
renderUI({
  org_data = organization_data()

  selectInput(
    "org3_issue", 
    label = "Issue Area:",
    choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
    # selected = "Human rights",
    selected = ifelse(
      sum(org_data[5:7,4]) == 0, "Emergency response",
      as.character(org_data[5:7,][which(org_data[5:7,4] == 1), 1])
    ),
    width = "450px"
  )

})

# Financial transparency
renderUI({
  org_data = organization_data()

  selectInput(
    "org3_fin_trans",
    label = "Financial Transparency:",
    choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
    # selected = "Engages in financial transparency",
    selected = ifelse(
      sum(org_data[8,4]) == 0, "Doesn’t engage in financial transparency",
      as.character(org_data[8,][which(org_data[8,4] == 1), 1])
    ),
    width = "450px"
  )

})

# Financial accountability
renderUI({
  org_data = organization_data()

  selectInput(
    "org3_fin_account",
    label = "Financial Accountability:",
    choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
    # selected = "Engages in financial accountability",
    selected = ifelse(
      sum(org_data[9,4]) == 0, "Doesn’t engage in financial accountability",
      as.character(org_data[9,][which(org_data[9,4] == 1), 1])
    ),
    width = "450px"
  )

})

# Funding sources
renderUI({
  org_data = organization_data()

  selectInput(
    "org3_funding",
    label = "Funding Source:",
    choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
    # selected = "Many small private donations",
    selected = ifelse(
      sum(org_data[10:11,4]) == 0, "Many small private donations",
      as.character(org_data[10:11,][which(org_data[10:11,4] == 1), 1])
    ),
    width = "450px"
  )

})

# Relationship with host government
renderUI({
  org_data = organization_data()

  selectInput(
    "org3_host_gov",
    label = "Relationship With Host Government",
    choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
    # selected = "Friendly relationship with government",
    selected = ifelse(
      sum(org_data[12:13,4]) == 0, "Friendly relationship with government",
      as.character(org_data[12:13,][which(org_data[12:13,4] == 1), 1])
    ),
    width = "450px"
  )
})
```

@@

# Organization
renderUI({
  org_data = organization_data()

  selectInput(
    "org4_org",
    label = "Organization:",
    choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
    # selected = "Red Cross",
    selected = as.character(org_data[1:4,][which(org_data[1:4,5] == 1), 1]),
    width = "450px"
  )

})

# Issue area
renderUI({
  org_data = organization_data()

  selectInput(
    "org4_issue", 
    label = "Issue Area:",
    choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
    # selected = "Refugee relief",
    selected = ifelse(
      sum(org_data[5:7,5]) == 0, "Emergency response",
      as.character(org_data[5:7,][which(org_data[5:7,5] == 1), 1])
    ),
    width = "450px"
  )

})

# Financial transparency
renderUI({
  org_data = organization_data()

  selectInput(
    "org4_fin_trans",
    label = "Financial Transparency:",
    choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
    # selected = "Engages in financial transparency",
    selected = ifelse(
      sum(org_data[8,5]) == 0, "Doesn’t engage in financial transparency",
      as.character(org_data[8,][which(org_data[8,5] == 1), 1])
    ),
    width = "450px"
  )

})

# Financial accountability
renderUI({
  org_data = organization_data()

  selectInput(
    "org4_fin_account",
    label = "Financial Accountability:",
    choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
    # selected = "Engages in financial accountability",
    selected = ifelse(
      sum(org_data[9,5]) == 0, "Doesn’t engage in financial accountability",
      as.character(org_data[9,][which(org_data[9,5] == 1), 1])
    ),
    width = "450px"
  )

})

# Funding sources
renderUI({
  org_data = organization_data()

  selectInput(
    "org4_funding",
    label = "Funding Source:",
    choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
    # selected = "Many small private donations",
    selected = ifelse(
      sum(org_data[10:11,5]) == 0, "Many small private donations",
      as.character(org_data[10:11,][which(org_data[10:11,5] == 1), 1])
    ),
    width = "450px"
  )

})

# Relationship with host government
renderUI({
  org_data = organization_data()

  selectInput(
    "org4_host_gov",
    label = "Relationship With Host Government",
    choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
    # selected = "Friendly relationship with government",
    selected = ifelse(
      sum(org_data[12:13,5]) == 0, "Friendly relationship with government",
      as.character(org_data[12:13,][which(org_data[12:13,5] == 1), 1])
    ),
    width = "450px"
  )

})
```

@@

# Follow national news
selectInput(
  "per1_national_news",
  label = "Follow national news:",
  choices = c("Rarely", "Once a week", "At least once a day"),
  # selected = "At least once a day",
  selected = ifelse(
    sum(persona_data[2:3,2]) == 0, "Rarely",
    as.character(persona_data[2:3,][which(persona_data[2:3,2] == 1), 1])
  ),
  width = "450px"
)

# Follow international news
selectInput(
  "per1_international_news",
  label = "Follow international news:",
  choices = c("Never", "Sometimes", "Always"),
  # selected = "Always",
  selected = ifelse(
    sum(persona_data[4:5,2]) == 0, "Never",
    as.character(persona_data[4:5,][which(persona_data[4:5,2] == 1), 1])
  ),
  width = "450px"
)

# Mediums to follow news
selectInput(
  "per1_news_medium",
  label = "Medium to follow news:",
  choices = c(
    "TV",
    "Print",
    "Online (not social media)",
    "Social media",
    "Radio",
    "Email newsletter",
    "News app"
  ),
  multiple = TRUE,
  # selected = c("TV", "Print", "Social media"),
  selected = deframe(persona_data[6:12,][which(persona_data[6:12,2] == 1), 1]),
  width = "450px"
)

>>>>

# Organization configuration
organization_data <- reactive({
  if (is.null(input$org_update$datapath)) {
    organization_data <- read_csv(
      here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
    )
  } else {
    organization_data <- read_csv(input$org_update$datapath)
  }
})

# Persona configuration
persona_data <- reactive({
  if (is.null(input$per_update$datapath)) {
    persona_data <- read_csv(
      here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
    )
  } else {
    persona_data <- read_csv(input$per_update$datapath)
  }
})
```

```{r organization-reactive-table}
# Assign level labels
org_table <- data.frame(
  levels = c(
    # Organization
    "Amnesty International",
    "Greenpeace", 
    "Oxfam", 
    "Red Cross",
    # Issue area
    "Environment", 
    "Human rights",
    "Refugee relief",
    # Financial transparency
    "Engages in financial transparency",
    # Financial accountability
    "Engages in financial accountability",
    # Funding sources
    "Handful of wealthy private donors", 
    "Government grants",
    # Relationship with host government
    "Criticized by government",
    "Under government crackdown"
  )
)

@@

  # Organization 4
  org_table$org4_value <- 0
  org_table$org4_value[org_table$levels %in% input$org4_org] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_issue] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_fin_trans] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_fin_account] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_funding] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_host_gov] <- 1
  org_table
})
```

@@

  # Persona 3
  per_table$per3_value <- 0
  per_table$per3_value[per_table$levels == 'Intercept'] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_national_news] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_international_news] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_news_medium] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_follow_gov] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_travel_developing] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_political_pref] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_institution_trust] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_others_charitable] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_worship_attendance] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religion_importance] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religion] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_charity_importance] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_trust_in_charity] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_donation_frequency] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_donation_amount] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_volunteer_12] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_volunteer_frequency] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_personal_activism] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_family_activism] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religious_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_sport_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_art_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_labor_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_political_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_environmental_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_professional_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_humanitarian_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_consumer_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_other_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_gender] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_marital_status] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_education] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_income] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_race] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_age] <- 1
  per_table
})
```

@@

```{r org1-inputs}
# Naming
textInput(
  "org1_name",
  label = "Organization Name:",
  value = "Organization 1",
  placeholder = "Enter Organization Name",
  width = "450px"
)

# Organization
renderUI({
  org_data = organization_data()
  selectInput(
    "org1_org",
    label = "Organization:",
    choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
    # selected = "Red Cross",
    selected = as.character(org_data[1:4,][which(org_data[1:4,2] == 1), 1]),
    width = "450px"
  )
})

# Issue area
renderUI({
  org_data = organization_data()
  selectInput(
    "org1_issue", 
    label = "Issue Area:",
    choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
    # selected = "Emergency response",
    selected = ifelse(
      sum(org_data[5:7,2]) == 0, "Emergency response",
      as.character(org_data[5:7,][which(org_data[5:7,2] == 1), 1])
    ),
    width = "450px"
  )
})

# Financial transparency
renderUI({
  org_data = organization_data()
  selectInput(
    "org1_fin_trans",
    label = "Financial Transparency:",
    choices = c(
      "Doesn’t engage in financial transparency", 
      "Engages in financial transparency"
    ),
    # selected = "Engages in financial transparency",
    selected = ifelse(
      sum(org_data[8,2]) == 0, "Doesn’t engage in financial transparency",
      as.character(org_data[8,][which(org_data[8,2] == 1), 1])
    ),
    width = "450px"
  )
})

# Financial accountability
renderUI({
  org_data = organization_data()
  selectInput(
    "org1_fin_account",
    label = "Financial Accountability:",
    choices = c(
      "Doesn’t engage in financial accountability", 
      "Engages in financial accountability"
    ),
    # selected = "Engages in financial accountability",
    selected = ifelse(
      sum(org_data[9,2]) == 0, "Doesn’t engage in financial accountability",
      as.character(org_data[9,][which(org_data[9,2] == 1), 1])
    ),
    width = "450px"
  )
})

# Funding sources
renderUI({
  org_data = organization_data()
  selectInput(
    "org1_funding",
    label = "Funding Source:",
    choices = c(
      "Many small private donations", 
      "Handful of wealthy private donors", 
      "Government grants"
    ),
    # selected = "Many small private donations",
    selected = ifelse(
      sum(org_data[10:11,2]) == 0, "Many small private donations",
      as.character(org_data[10:11,][which(org_data[10:11,2] == 1), 1])
    ),
    width = "450px"
  )
})

# Relationship with host government
renderUI({
  org_data = organization_data()
  selectInput(
    "org1_host_gov",
    label = "Relationship With Host Government",
    choices = c(
      "Friendly relationship with government", 
      "Criticized by government",  
      "Under government crackdown"
    ),
    # selected = "Friendly relationship with government",
    selected = ifelse(
      sum(org_data[12:13,2]) == 0, "Friendly relationship with government",
      as.character(org_data[12:13,][which(org_data[12:13,2] == 1), 1])
    ),
    width = "450px"
  )
})
```

@@

# Organization
renderUI({
  org_data = organization_data()
  selectInput(
    "org2_org",
    label = "Organization:",
    choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
    # selected = "Red Cross",
    selected = as.character(org_data[1:4,][which(org_data[1:4,3] == 1), 1]),
    width = "450px"
  )
})

# Issue area
renderUI({
  org_data = organization_data()
  selectInput(
    "org2_issue", 
    label = "Issue Area:",
    choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
    # selected = "Environment",
    selected = ifelse(
      sum(org_data[5:7,3]) == 0, "Emergency response",
      as.character(org_data[5:7,][which(org_data[5:7,3] == 1), 1])
    ),
    width = "450px"
  )
})

# Financial transparency
renderUI({
  org_data = organization_data()
  selectInput(
    "org2_fin_trans",
    label = "Financial Transparency:",
    choices = c(
      "Doesn’t engage in financial transparency", 
      "Engages in financial transparency"
    ),
    # selected = "Engages in financial transparency",
    selected = ifelse(
      sum(org_data[8,3]) == 0, "Doesn’t engage in financial transparency",
      as.character(org_data[8,][which(org_data[8,3] == 1), 1])
    ),
    width = "450px"
  )
})

# Financial accountability
renderUI({
  org_data = organization_data()
  selectInput(
    "org2_fin_account",
    label = "Financial Accountability:",
    choices = c(
      "Doesn’t engage in financial accountability", 
      "Engages in financial accountability"
    ),
    # selected = "Engages in financial accountability",
    selected = ifelse(
      sum(org_data[9,3]) == 0, "Doesn’t engage in financial accountability",
      as.character(org_data[9,][which(org_data[9,3] == 1), 1])
    ),
    width = "450px"
  )
})

# Funding sources
renderUI({
  org_data = organization_data()
  selectInput(
    "org2_funding",
    label = "Funding Source:",
    choices = c(
      "Many small private donations", 
      "Handful of wealthy private donors", 
      "Government grants"
    ),
    # selected = "Many small private donations",
    selected = ifelse(
      sum(org_data[10:11,3]) == 0, "Many small private donations",
      as.character(org_data[10:11,][which(org_data[10:11,3] == 1), 1])
    ),
    width = "450px"
  )
})

# Relationship with host government
renderUI({
  org_data = organization_data()
  selectInput(
    "org2_host_gov",
    label = "Relationship With Host Government",
    choices = c(
      "Friendly relationship with government", 
      "Criticized by government",  
      "Under government crackdown"
    ),
    # selected = "Friendly relationship with government",
    selected = ifelse(
      sum(org_data[12:13,3]) == 0, "Friendly relationship with government",
      as.character(org_data[12:13,][which(org_data[12:13,3] == 1), 1])
    ),
    width = "450px"
  )
})
```

@@

# Organization
renderUI({
  org_data = organization_data()
  selectInput(
    "org3_org",
    label = "Organization:",
    choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
    # selected = "Red Cross",
    selected = as.character(org_data[1:4,][which(org_data[1:4,4] == 1), 1]),
    width = "450px"
  )
})

# Issue area
renderUI({
  org_data = organization_data()
  selectInput(
    "org3_issue", 
    label = "Issue Area:",
    choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
    # selected = "Human rights",
    selected = ifelse(
      sum(org_data[5:7,4]) == 0, "Emergency response",
      as.character(org_data[5:7,][which(org_data[5:7,4] == 1), 1])
    ),
    width = "450px"
  )
})

# Financial transparency
renderUI({
  org_data = organization_data()
  selectInput(
    "org3_fin_trans",
    label = "Financial Transparency:",
    choices = c(
      "Doesn’t engage in financial transparency", 
      "Engages in financial transparency"
    ),
    # selected = "Engages in financial transparency",
    selected = ifelse(
      sum(org_data[8,4]) == 0, "Doesn’t engage in financial transparency",
      as.character(org_data[8,][which(org_data[8,4] == 1), 1])
    ),
    width = "450px"
  )
})

# Financial accountability
renderUI({
  org_data = organization_data()
  selectInput(
    "org3_fin_account",
    label = "Financial Accountability:",
    choices = c(
      "Doesn’t engage in financial accountability", 
      "Engages in financial accountability"
    ),
    # selected = "Engages in financial accountability",
    selected = ifelse(
      sum(org_data[9,4]) == 0, "Doesn’t engage in financial accountability",
      as.character(org_data[9,][which(org_data[9,4] == 1), 1])
    ),
    width = "450px"
  )
})

# Funding sources
renderUI({
  org_data = organization_data()
  selectInput(
    "org3_funding",
    label = "Funding Source:",
    choices = c(
      "Many small private donations", 
      "Handful of wealthy private donors", 
      "Government grants"
    ),
    # selected = "Many small private donations",
    selected = ifelse(
      sum(org_data[10:11,4]) == 0, "Many small private donations",
      as.character(org_data[10:11,][which(org_data[10:11,4] == 1), 1])
    ),
    width = "450px"
  )
})

# Relationship with host government
renderUI({
  org_data = organization_data()
  selectInput(
    "org3_host_gov",
    label = "Relationship With Host Government",
    choices = c(
      "Friendly relationship with government", 
      "Criticized by government",  
      "Under government crackdown"
    ),
    # selected = "Friendly relationship with government",
    selected = ifelse(
      sum(org_data[12:13,4]) == 0, "Friendly relationship with government",
      as.character(org_data[12:13,][which(org_data[12:13,4] == 1), 1])
    ),
    width = "450px"
  )
})
```

@@

# Organization
renderUI({
  org_data = organization_data()
  selectInput(
    "org4_org",
    label = "Organization:",
    choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
    # selected = "Red Cross",
    selected = as.character(org_data[1:4,][which(org_data[1:4,5] == 1), 1]),
    width = "450px"
  )
})

# Issue area
renderUI({
  org_data = organization_data()
  selectInput(
    "org4_issue", 
    label = "Issue Area:",
    choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
    # selected = "Refugee relief",
    selected = ifelse(
      sum(org_data[5:7,5]) == 0, "Emergency response",
      as.character(org_data[5:7,][which(org_data[5:7,5] == 1), 1])
    ),
    width = "450px"
  )
})

# Financial transparency
renderUI({
  org_data = organization_data()
  selectInput(
    "org4_fin_trans",
    label = "Financial Transparency:",
    choices = c(
      "Doesn’t engage in financial transparency", 
      "Engages in financial transparency"
    ),
    # selected = "Engages in financial transparency",
    selected = ifelse(
      sum(org_data[8,5]) == 0, "Doesn’t engage in financial transparency",
      as.character(org_data[8,][which(org_data[8,5] == 1), 1])
    ),
    width = "450px"
  )
})

# Financial accountability
renderUI({
  org_data = organization_data()
  selectInput(
    "org4_fin_account",
    label = "Financial Accountability:",
    choices = c(
      "Doesn’t engage in financial accountability", 
      "Engages in financial accountability"
    ),
    # selected = "Engages in financial accountability",
    selected = ifelse(
      sum(org_data[9,5]) == 0, "Doesn’t engage in financial accountability",
      as.character(org_data[9,][which(org_data[9,5] == 1), 1])
    ),
    width = "450px"
  )
})

# Funding sources
renderUI({
  org_data = organization_data()
  selectInput(
    "org4_funding",
    label = "Funding Source:",
    choices = c(
      "Many small private donations", 
      "Handful of wealthy private donors", 
      "Government grants"
    ),
    # selected = "Many small private donations",
    selected = ifelse(
      sum(org_data[10:11,5]) == 0, "Many small private donations",
      as.character(org_data[10:11,][which(org_data[10:11,5] == 1), 1])
    ),
    width = "450px"
  )
})

# Relationship with host government
renderUI({
  org_data = organization_data()
  selectInput(
    "org4_host_gov",
    label = "Relationship With Host Government",
    choices = c(
      "Friendly relationship with government", 
      "Criticized by government",  
      "Under government crackdown"
    ),
    # selected = "Friendly relationship with government",
    selected = ifelse(
      sum(org_data[12:13,5]) == 0, "Friendly relationship with government",
      as.character(org_data[12:13,][which(org_data[12:13,5] == 1), 1])
    ),
    width = "450px"
  )
})
```

@@

# Follow national news
renderUI({
  per_data = persona_data()
  selectInput(
    "per1_national_news",
    label = "Follow national news:",
    choices = c("Rarely", "Once a week", "At least once a day"),
    # selected = "At least once a day",
    selected = ifelse(
      sum(per_data[2:3,2]) == 0, "Rarely",
      as.character(per_data[2:3,][which(per_data[2:3,2] == 1), 1])
    ),
    width = "450px"
  )
})

# Follow international news
renderUI({
  per_data = persona_data()
  selectInput(
    "per1_international_news",
    label = "Follow international news:",
    choices = c("Never", "Sometimes", "Always"),
    # selected = "Always",
    selected = ifelse(
      sum(per_data[4:5,2]) == 0, "Never",
      as.character(per_data[4:5,][which(per_data[4:5,2] == 1), 1])
    ),
    width = "450px"
  )
})

# Mediums to follow news
renderUI({
  per_data = persona_data()
  selectInput(
    "per1_news_medium",
    label = "Medium to follow news:",
    choices = c(
      "TV",
      "Print",
      "Online (not social media)",
      "Social media",
      "Radio",
      "Email newsletter",
      "News app"
    ),
    multiple = TRUE,
    # selected = c("TV", "Print", "Social media"),
    selected = deframe(per_data[6:12,][which(per_data[6:12,2] == 1), 1]),
    width = "450px"
  )
})
